How to be a good member of a scientific software community [Article v\versionnumber]

### 2021-08-30 paper.tex
caught a typo
wording tweak

This paper is primarily aimed at junior scientists who are new to performing
computational research and inexperienced at asking for help. However, we hope it
will be valuable to anyone who uses software to do their research and struggles
to ask for help.

@@

If the justice perspective doesn't persuade you, consider the practical
consequences. Bad behavior on the part of developers of your project (or your
community in general) will drive users and developers away from you. If
interacting with your community is unpleasant, folks will either use alternative
codes or use your code but not cite you. The next person with an idea for an
innovative new feature will add it to a different package, or won't do it at
all (hurting the whole community). Ask yourself: can your project really afford to drive away talented hard-working people eager to help? Is it worth is, just so a few people don't have to engage with basic courtesy?

>>>>

This paper is primarily aimed at junior scientists who are new to performing
computational research and inexperienced at asking for help. However, we hope it
will be valuable to anyone who uses software written by others to do their
research.

@@

If the justice perspective doesn't persuade you, consider the practical
consequences. Bad behavior on the part of developers of your project (or your
community in general) will drive users and developers away from you. If
interacting with your community is unpleasant, folks will either use alternative
codes or use your code but not cite you. The next person with an idea for an
innovative new feature will add it to a different package, or won't do it at
all (hurting the whole community). Ask yourself: can your project really afford to drive away talented hard-working people eager to help? Is it worth it, just so a few people don't have to engage with basic courtesy?
